\chapter{Collision Detection}%
\label{chap:collision_detection}

	There are several types of collision that may occur in a \glspl{cdpr}. These
	are:

	\begin{enumerate}

		\item Cable-Cable collisions

		\item Cable-Obstacle collisions

		\item Cable-End-Effector collisions

		\item End-Effector-Obstacle collisions

	\end{enumerate}

	The following assumptions were made for the collision-detection
	algorithms:

	\begin{enumerate}

		\item

			Cables are modelled as straight lines. If the tension in the cables
			is sufficiently high, this assumption is satisfied. The current
			collision-detection algorithms make no attempt to detect collisions
			in sagging cables.

		\item

			The end-effector and the obstacles are approximated as convex
			polyhedra. To ensure a safety margin, obstacles are usually modelled
			to be slightly larger than they are in reality. This justifies the
			use of convex  shapes to approximate them. For cases where modelling
			an obstacle as a convex shape is unnecessarily wasteful, a
			non-convex obstacle can be built up out of the union of convex
			obstacles.

	\end{enumerate}

	The current chapter discusses the algorithms used to detect these classes of
	collisions.

	\input{chapters/collision_detection/subs/cable_cable}
	\input{chapters/collision_detection/subs/cable_obstacle}
	\input{chapters/collision_detection/subs/cable_end_effector}
	\input{chapters/collision_detection/subs/end_effector_obstacle}
	\input{chapters/collision_detection/subs/capacity_margin}
	\input{chapters/collision_detection/subs/overall_algorithm}
